### 2020-01-01 methods.tex
added methods section

\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is some matrix Norm.  Here, we will consider:

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j}$,
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$, or even the
 \item $\alpha-$Norm (or Shatten Norm) $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

where $\lambda_{i}$ is the $i-th$ eigenvalue of the correlation matrix $\mathbf{X}=\dfrac{1}{N}\mathbf{W}^{T}\mathbf{W}$, and $\lambda_{max}$ is the maximum eigenvalue.

@@

We will also consider an approximate capacity metric, $\hat{\alpha}$, shown previously to correlate well the reported test accuracy of pretrained DNNs

@@

which approxmiates the log $\alpha-$Norm for both Very Heavy Tailed weight matrices as well as finite size, Moderately Heavy Tailed $\mathbf{W}$.
---

CLARIFY HOW CONV2D lsyers are treated

----

\begin{eqnarray*}
\log\mathcal{C} &\sim& \log\bigg[\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert\bigg]  \\
                &\sim& \bigg[\log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert\cdots\log\Vert\mathbf{W}_{L}\Vert\bigg]  ,
\end{eqnarray*}
and we define the average log norm of the weight matrices as

>>>>

\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is a matrix norm.   We will actually compute the log Complexity, which takes the form 
of an Average Log Norm:
\begin{eqnarray*}
\log\mathcal{C} &\sim& \log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert\cdots\log\Vert\mathbf{W}_{L}\Vert
\end{eqnarray*}

Here, we will consider the following Norms:

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j}$
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
 \item $\alpha-$Norm (or Shatten Norm) $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

where $\lambda_{i}$ is the $i-th$ eigenvalue of the correlation matrix $\mathbf{X}=\dfrac{1}{N}\mathbf{W}^{T}\mathbf{W}$, and $\lambda_{max}$ is the maximum eigenvalue.   (Note that eigenvalues are the square of the singular values $\sigma_{i}$ of $\mathbf{W}$ :  $\lambda_{i}=\sigma^{2}_{i}$.)

@@

We will also consider an approximate capacity metric, $\hat{\alpha}$, shown previously to correlate well with the trends in reported test accuracies of pretrained DNNs \cite{MM}

@@

which approximates the log $\alpha-$Norm for both Very Heavy Tailed weight matrices ($alpha < 2$  and reasoably well for finite size, Moderately Heavy Tailed ones $\alpha\in[2,5]$.

SOME MORE DISCUSSION HERE

\paragraph{Spectral Analysis of Convolutional 2D Layers}
While we can easily analyze Linear layers, there is some ambiguity in performing spectral analysis on Convolutional 2D (Conv2D) layers.  A Conv2D layer is a 4-index tensor of dimension $(w,h,in\_ch,out\_ch)$.  
Typically, the $w=h=k$, giving $(k\times k)$ Feature Maps of dimension $(in\_ch\times out\_ch)$ each. 
Usually $in\_ch\ll out\_ch$.
There are at least 3 different approaches to computing the Singular Values Decomposition(s) (SVD) of an Conv2D layer
\begin{enumerate}
\item run SVD on each of the feature maps, yielding $(k\times k)$ sets of $M$ singular values. 
\item stack the feature maps into a single rectangular matrix of, say, dimension $((k\times k\times out\_ch)\times in\_ch)$, yielding $in\_ch$ singular values
\item Compute the 2D Fourier Transform (FFT) for each of the $(in\_ch, out\_ch)$ pairs, and run SVD on the resulting Fourier coeffients\cite{Long2019}.  This leads to $(k\times in\_ch\times out\_ch)$ non-zero singular values.\footnote{assuming say no padding and a stride of 1}
\end{enumerate}

Each method has tradeoffs. For this study, because we are computing tens of thousands of calculations,  we select $1.$, which is numerically the fastest. 
----
